**Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces**

### 2021-08-10 submission/manuscript.Rmd
Editor review done.

### DNA isolation
DNA from surfaces of *C. nodosa* and *C. cylindracea* was isolated from a pool of leaves or thalli on the sampling day using a previously modified and adapted protocol that allows for a selective epiphytic DNA isolation [@Korlevic2021; @Massana1997]. Briefly, leaves and thalli were incubated in a lysis buffer and treated with lysozyme and proteinase K. Following the incubations, the mixture containing lysed epiphytic cells was separated from the leaves and thalli and extracted using phenol-chloroform. Finally, the extracted DNA was precipitated using isopropanol. DNA from seawater picoplankton was extracted from 0.2 \si{\um} polycarbonate filters according to @Massana1997 with a slight modification. Following the phenol-chloroform extraction, 1/10 of 3 \si{\Molar} sodium acetate (pH 5.2) was added. DNA was precipitated by adding 1 volume of chilled isopropanol, incubating the mixtures overnight at \num{-20} \si{\degreeCelsius} and centrifuging at 20,000 × *g* and 4 \si{\degreeCelsius} for 20 \si{\minute}. The pellet was washed twice with 500 \si{\ul} of chilled 70 \si{\percent} ethanol and centrifuged after each washing step at 20,000 × *g* and 4 \si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were re-suspended in 50 -- 100 \si{\ul} of deionized water.

@@

\newpage
## Results

@@

## Acknowledgments
This work was funded by the Croatian Science Foundation through the MICRO-SEAGRASS project (project number IP-2016-06-7118). ZZ and GJH were supported by the Austrian Science Fund (FWF) project ARTEMIS (project number P28781-B21). We would like to thank Margareta Buterer for technical support, Paolo Paliaga for help during sampling and the University Computing Center of the University of Zagreb for access to the computer cluster Isabella.

>>>>

### DNA isolation
DNA from surfaces of *C. nodosa* and *C. cylindracea* was isolated from a pool of leaves (1 g wet weight) or thalli (2 g wet weight) on the sampling day using a previously modified and adapted protocol that allows for a selective epiphytic DNA isolation [@Korlevic2021; @Massana1997]. Briefly, leaves and thalli were incubated in a lysis buffer and treated with lysozyme and proteinase K. Following the incubations, the mixture containing lysed epiphytic cells was separated from the leaves and thalli and extracted using phenol-chloroform. Finally, the extracted DNA was precipitated using isopropanol. DNA from seawater picoplankton was extracted from 0.2 \si{\um} polycarbonate filters according to @Massana1997 with a slight modification. Following the phenol-chloroform extraction, 1/10 of 3 \si{\Molar} sodium acetate (pH 5.2) was added. DNA was precipitated by adding 1 volume of chilled isopropanol, incubating the mixtures overnight at \num{-20} \si{\degreeCelsius} and centrifuging at 20,000 × *g* and 4 \si{\degreeCelsius} for 20 \si{\minute}. The pellet was washed twice with 500 \si{\ul} of chilled 70 \si{\percent} ethanol and centrifuged after each washing step at 20,000 × *g* and 4 \si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were re-suspended in 50 -- 100 \si{\ul} of deionized water. One DNA sample originating from seawater picoplankton was obtained per each sampling point.

@@

## Results

@@

\newpage
## Acknowledgments
This work was funded by the Croatian Science Foundation through the MICRO-SEAGRASS project (project number IP-2016-06-7118). ZZ and GJH were supported by the Austrian Science Fund (FWF) project ARTEMIS (project number P28781-B21). We would like to thank Margareta Buterer for technical support, Paolo Paliaga for help during sampling and the University Computing Center of the University of Zagreb for access to the computer cluster Isabella.
